---
title: "Findings"
output: html_document
---

Findings

Median ATS Ratio by Income Decile
```{r}
tapply(resdata$atsratio,resdata$IncomeDecile, summary)
```

    - The Median Assessment to Sale ratio increases as the Median Income of the tract Increase
    
    - As the income increases, the assessment approaches the sale value of the house
    
    - 


Median ATS Ratio by Sales Decile
```{r}
tapply(resdata$atsratio, resdata$salesdecile, summary)
```

    - The Median Assessment to Sale ratio decreases as the sale price increases
    
    - As the sale price of a house increases, the assessment diverges from the sale value of the house
    
    - Higher prices homes are under assessed  
    
    
Median ATS Ratio by Percent Black Population Decile
```{r}
blackpop <- tapply(resdata$atsratio,resdata$blackdecile, summary)

medians <- c()
deciles <- 1:10
for (i in 1:10){
  medians[i] <- as.numeric(blackpop[[i]]['Median']) }

BlackATS <- data.frame("Medians" = medians,
                       "Deciles" = deciles)

lm(Medians ~ Deciles,data=BlackATS);anova(lm(Medians ~ Deciles,data=BlackATS))
```

    - The Median Assessment to Sale ratio decreases as the percent black population increases
    
    - As the percent of the black population increases in a tract, the assessment diverges from the sale value of the house
    
    - Homes in black neighborhoods are under assessed 
    
    
Median ATS Ratio by Percent White Population Decile
```{r}
tapply(resdata$atsratio,resdata$whitedecile, summary)
whitepop <- tapply(resdata$atsratio,resdata$whitedecile, summary)

medians <- c()
deciles <- 1:10
for (i in 1:10){
  medians[i] <- as.numeric(whitepop[[i]]['Median']) }

WhiteATS <- data.frame("Medians" = medians,
                       "Deciles" = deciles)

lm(Medians ~ Deciles,data=WhiteATS);anova(lm(Medians ~ Deciles,data=WhiteATS))
```

    - The Median Assessment to Sale ratio increases as the percent white population increases
    
    - As the percent of the white population increases in a tract, the assessment approaches the sale value of the house
    
    - Homes in white neighborhoods are over assessed (relative to black neighborhoods), homes are assessed closer to their true sale value
    
    - Homes in white neighborhoods show the opposite trend to black neighborhoods
    
    
Median ATS Ratio by Percent Hispanic Population Decile
```{r}
tapply(resdata$atsratio, resdata$hispaniddecile, summary)
hispanicpop <- tapply(resdata$atsratio, resdata$hispaniddecile, summary)

medians <- c()
deciles <- 1:10
for (i in 1:10){
  medians[i] <- as.numeric(hispanicpop[[i]]['Median']) }

HispATS <- data.frame("Medians" = medians,
                       "Deciles" = deciles)

lm(Medians ~ Deciles,data=HispATS);anova(lm(Medians ~ Deciles,data=HispATS))
```


    - See less of a trend here
